### 2011-05-12 paper.tex
added to intro
minor fix

In this paper we work to reproduce several classical complexity theoretic results explicitly in the context of promise problems, which we represent as partial functions. We introduce several operators, based on their analogues for languages and use them to establish analogues of several standard results.

@@

In this paper, we will want to concern ourselves mainly with $\p$ and classes that result from applying a sequence of the above operators to it. We will use the following terminology throughout.
\begin{definition}\label{constructible}
For a set $Q$ of operators, we say a complexity class $C$ is \emph{$Q$-constructible} if it is of the form $Q_k \cdot Q_{k-1} \cdots Q_{2} \cdot Q_1 \cdot \p$ for some $k$ where $Q_i \in Q$ for all $i \in \{1,\ldots,k\}$.
\end{definition}

>>>>

In this paper we work to reproduce several classical complexity theoretic results explicitly in the context of promise problems, which we represent as partial functions. We introduce several operators, based on their analogues for languages and use them to establish analogues of several standard results. In particular, we will prove that probabilities can be amplified, not just in $\bpp$, but in more general classes which contain randomness.

@@

In this paper, we will want to concern ourselves mainly with $\p$ and classes that result from applying a sequence of the above operators to it. We will use the following terminology throughout.
\begin{definition}\label{constructible}
For a set $Q$ of operators, we say a complexity class $C$ is \emph{$Q$-constructible} if it is of the form $\op_k \cdot\op_{k-1} \cdots \op_{2} \cdot \op_1 \cdot \p$ for some $k$ where $\op_i \in Q$ for all $i \in \{1,\ldots,k\}$.
\end{definition}
